Morality, politics, and cooperation

### 2021-11-11 manuscript/manuscript.Rmd
finish tris analyses

---
title: "Morality, politics, and cooperation"
output: bookdown::html_document2
date: '`r format(Sys.time(), "%d %B, %Y")`'
bibliography: references.bib
knit: worcs::cite_all
---

```{r setup, include=FALSE}
# We recommend that you prepare your raw data for analysis in 'prepare_data.R',
# and end that file with either open_data(yourdata), or closed_data(yourdata).
# Then, uncomment the line below to load the original or synthetic data
# (whichever is available), to allow anyone to reproduce your code:
library("worcs")
knitr::opts_chunk$set(echo = FALSE, results = "hide", message = FALSE, warning = FALSE)
options(knitr.kable.NA = '')
library(ggplot2)
library(tidySEM)
library(lavaan)
library(semTools)
library(kableExtra)
library(bookdown)
library(psych)
dat <- load_data(to_envir = FALSE)
source("../scales_list.R")
scales_list <- lapply(scales_list, function(i){
  tmp <- lapply(names(i), function(j){ paste0(j, "_", 1:length(i[[j]]))})
  names(tmp) <- names(i)
  tmp
  })
set.seed(1)
cfas <- lapply(names(scales_list), function(cnt){
  results <- t(sapply(scales_list[[cnt]], function(scal){
    out <- cfa(paste0("F =~ ", paste0(scal, collapse = "+")), std.lv = TRUE, data = dat[[cnt]])
    paran <- fa.parallel(dat[[cnt]][, scal])
    tab <- table_results(out, columns = NULL, digits=3)
    tab <- tab[-nrow(tab), ]
    loadns <- as.numeric(tab$est_std)[tab$op == "=~"]
    r2s <- lavInspect(out, "r2")
    omga <- semTools::reliability(out, what = "omega")[1,1]
    c(Subscale = gsub("_\\d$", "", scal[1]),
      Items = length(scal),
      n = out@Data@nobs[[1]],
      formatC(unlist(table_fit(out)[1, c("chisq", "cfi", "tli", "rmsea", "srmr")]), digits = 3, format = "f"), 
      formatC(c(min_load = min(loadns), max_load = max(loadns), min_r2 = min(r2s), max_r2 = max(r2s), omega = omga), digits = 3, format = "f"),
      Reliability = tidySEM:::interpret(omga),
      Factors = fa.parallel(dat[[cnt]][,scal]) $nfact
      )
  }))
})
names(cfas) <- names(scales_list)
```

@@

>>>>

---
title: "Morality, politics, and cooperation"
output:
  bookdown::html_document2:
    keep_md: yes
date: '`r format(Sys.time(), "%d %B, %Y")`'
bibliography: references.bib
knit: worcs::cite_all
---

```{r setup, include=FALSE}
# We recommend that you prepare your raw data for analysis in 'prepare_data.R',
# and end that file with either open_data(yourdata), or closed_data(yourdata).
# Then, uncomment the line below to load the original or synthetic data
# (whichever is available), to allow anyone to reproduce your code:
library("worcs")
knitr::opts_chunk$set(echo = FALSE, results = "hide", message = FALSE, warning = FALSE)
options(knitr.kable.NA = '')
library(ggplot2)
library(tidySEM)
library(lavaan)
library(semTools)
library(kableExtra)
library(bookdown)
library(psych)
dat <- load_data(to_envir = FALSE)[1:3]
source("../scales_list.R")
scales_list <- lapply(scales_list, function(i){
  tmp <- lapply(names(i), function(j){ paste0(j, "_", 1:length(i[[j]]))})
  names(tmp) <- names(i)
  tmp
  })
set.seed(1)
cfas <- lapply(names(scales_list), function(cnt){
  results <- t(sapply(scales_list[[cnt]], function(scal){
    out <- cfa(paste0("F =~ ", paste0(scal, collapse = "+")), std.lv = TRUE, data = dat[[cnt]])
    paran <- fa.parallel(dat[[cnt]][, scal])
    tab <- table_results(out, columns = NULL, digits=3)
    tab <- tab[-nrow(tab), ]
    loadns <- as.numeric(tab$est_std)[tab$op == "=~"]
    r2s <- lavInspect(out, "r2")
    omga <- semTools::reliability(out, what = "omega")[1,1]
    c(Subscale = gsub("_\\d$", "", scal[1]),
      Items = length(scal),
      n = out@Data@nobs[[1]],
      formatC(unlist(table_fit(out)[1, c("chisq", "cfi", "tli", "rmsea", "srmr")]), digits = 3, format = "f"), 
      formatC(c(min_load = min(loadns), max_load = max(loadns), min_r2 = min(r2s), max_r2 = max(r2s), omega = omga), digits = 3, format = "f"),
      Reliability = tidySEM:::interpret(omga),
      Factors = fa.parallel(dat[[cnt]][,scal]) $nfact
      )
  }))
})
names(cfas) <- names(scales_list)
```

@@

# Exploratory analyses

The preceding analyses were conceptually replicated in a fourth sample.
Note that this sample used moral relevance scales instead of moral judgment scales.

```{r, include = FALSE, code=xfun::read_utf8('../analysis_tris.R')}

This replication offered no support for any hypothesis except H`r which(bayesfactors_tris > 3)`:

```{r, results = "asis"}
trisfit <- unlist(table_fit(res_tris)[1, c("chisq", "cfi", "tli", "rmsea", "srmr")])
for(i in 1:length(bayesfactors_tris)){
  cat(
    "* $BF_{h", i, "} = ", formatC(bayesfactors_tris[i], digits = 3, format = "f"),
    "$, based on parameters ", 
    paste0(names(est_for_hyp_tris[[i]]), " (", formatC(est_for_hyp_tris[[i]], digits = 3, format = "f"), ")", collapse = ", "), ".  \r\n",
    sep = ""
  )
}
```

The fit of this model was also poor, though somewhat better than for the confirmatory analyses; `r paste0(names(trisfit), " = ", formatC(trisfit, digits = 3, format = "f"), collapse = ", ")`.
